---
title: "Exploratory analysis of Perceptions about Science and Open Science"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(dev = "png",
                      fig.path = "../images/",
                      dpi = 300)
```

## Loading the neccesary libraries
```{r, message=FALSE, warning=FALSE}
library(readr)        # load csv
library(HH)           # likert plotting
```

First, we load the tables.
```{r, message=FALSE, warning=FALSE}
science <- read_csv("../data/cleaned/science.csv")
experience <- read_csv("../data/cleaned/experience.csv")
efficiency <- read_csv("../data/cleaned/efficiency.csv")
```

We add a function to set percentages in plots.
```{r}
#origNames = colnames(data)
panel <- function(...){
  panel.likert(...)
  vals <- list(...)
  DF <- data.frame(x=vals$x, y=vals$y, groups=vals$groups)
  grps <- as.character(DF$groups)
  for(i in 1:length(origNames)){
    grps <- sub(paste0('^',origNames[i]),i,grps)
  }
  DF <- DF[order(DF$y,grps),]
  DF$correctX <- ave(DF$x,DF$y,FUN=function(x){
    x[x < 0] <- rev(cumsum(rev(x[x < 0]))) - x[x < 0]/2
    x[x > 0] <- cumsum(x[x > 0]) - x[x > 0]/2
    return(x)
  })
  subs <- sub(' Positive$','',DF$groups)
  collapse <- subs[-1] == subs[-length(subs)] & DF$y[-1] == DF$y[-length(DF$y)]
  DF$abs <- abs(DF$x)
  DF$abs[c(collapse,FALSE)] <- DF$abs[c(collapse,FALSE)] + DF$abs[c(FALSE,collapse)]
  DF$correctX[c(collapse,FALSE)] <- 0
  DF <- DF[c(TRUE,!collapse),]
  DF$perc <- round(ave(DF$abs,DF$y,FUN=function(x){x/sum(x) * 100}), 0)
  DF$perc <- paste0(DF$perc,'%')
  DF$perc[DF$perc == "0%"] <- ""
  panel.text(x=DF$correctX, y=DF$y, label=DF$perc, cex=1)
}
```

We start by plotting the science table.
```{r science, out.width="100%", fig.height=20, fig.width=40}

likert(Measures ~ .,
       data=science,
       as.percent=TRUE,
       positive.order=TRUE,
       main=list("Valore cada una de las siguientes cuestiones relacionadas con su opinión sobre la ciencia", cex=3),
       rightAxis=F,
       ylab=NULL,
       panel=NULL,
       xlab=list("Percent", cex=2),
       auto.key=list(cex=2),
       scales=list(y=list(cex=2),
                            xlab=list(cex=2)
                   )
       )
```

Now the experience table.
```{r experience, out.width="100%", fig.height=20, fig.width=40}

likert(Measures ~ .,
       data=experience,
       as.percent=TRUE,
       positive.order=TRUE,
       main=list("Marque la opción que mejor represente su conocimiento y experiencia con cada práctica en los últimos 5 (cinco) años", cex=3),
       rightAxis=F,
       ylab=NULL,
       panel=NULL,
       xlab=list("Percent", cex=2),
       auto.key=list(cex=1.6),
       scales=list(y=list(cex=1.7),
                            xlab=list(cex=2)
                   )
       )
```

Finally, the efficiency table.
```{r efficiency, out.width="100%", fig.height=20, fig.width=40}

likert(Measures ~ .,
       data=efficiency,
       as.percent=TRUE,
       positive.order=TRUE,
       main=list("Elija la opción que mejor represente cuán importante considera que es cada una de las siguientes 
                 prácticas para mejorar la calidad y eficiencia de las investigaciones en su campo", cex=3),
       rightAxis=F,
       ylab=NULL,
       panel=NULL,
       xlab=list("Percent", cex=2),
       auto.key=list(cex=2),
       scales=list(y=list(cex=2),
                            xlab=list(cex=2)
                   )
       )
```





#### Plotting the science dataset


library(tidyverse)

plot_likert <- function(v1, v2, v3) {
  

plot_likert(Measures, science, )






```

#### Plotting the experience dataset
```{r experience, out.width="100%", fig.height=15, fig.width=40}
likert(Measures ~ .,
       data=experience,
       as.percent=TRUE,
       positive.order=TRUE,
       main="Marque la opción que mejor represente su conocimiento y experiencia con cada práctica en los últimos 5 (cinco) años",
       rightAxis=F,
       key.border.white=F,
       auto.key.in = list(cex=1.5),
       ylab=NULL,
       scales = list(y = list(cex = 1.5))) 
```

#### Plotting the efficiency dataset
```{r efficiency, out.width="100%", fig.height=15, fig.width=30}
likert(Measures ~ .,
       data=efficiency,
       as.percent=TRUE,
       positive.order=TRUE,
       main="Elija la opción que mejor represente cuán importante considera que es cada una de las siguientes prácticas para mejorar la calidad y eficiencia de las investigaciones en su campo",
       rightAxis=F,
       key.border.white=F,
       auto.key.in = list(cex=1.5),
       ylab=NULL,
       scales = list(y = list(cex = 1.5))) 
```

#### Plotting the science dataset by education
```{r significance_by_education, out.width="100%", fig.height=15, fig.width=30}
significance_by_education <- read_csv("../data/significance_by_education.csv")
origNames = colnames(significance_by_education)
myPanelFunc <- function(...){
  panel.likert(...)
  vals <- list(...)
  DF <- data.frame(x=vals$x, y=vals$y, groups=vals$groups)
  grps <- as.character(DF$groups)
  for(i in 1:length(origNames)){
    grps <- sub(paste0('^',origNames[i]),i,grps)
  }
  DF <- DF[order(DF$y,grps),]
  DF$correctX <- ave(DF$x,DF$y,FUN=function(x){
    x[x < 0] <- rev(cumsum(rev(x[x < 0]))) - x[x < 0]/2
    x[x > 0] <- cumsum(x[x > 0]) - x[x > 0]/2
    return(x)
  })
  subs <- sub(' Positive$','',DF$groups)
  collapse <- subs[-1] == subs[-length(subs)] & DF$y[-1] == DF$y[-length(DF$y)]
  DF$abs <- abs(DF$x)
  DF$abs[c(collapse,FALSE)] <- DF$abs[c(collapse,FALSE)] + DF$abs[c(FALSE,collapse)]
  DF$correctX[c(collapse,FALSE)] <- 0
  DF <- DF[c(TRUE,!collapse),]
  DF$perc <- round(ave(DF$abs,DF$y,FUN=function(x){x/sum(x) * 100}), 0)
  DF$perc <- paste0(DF$perc,'%')
  DF$perc[DF$perc == "0%"] <- ""
  panel.text(x=DF$correctX, y=DF$y, label=DF$perc, cex=1)
}
likert(education ~ .,
       data=significance_by_education,
       as.percent=TRUE,
       positive.order=TRUE,
       main="Gran parte de los investigadores solamente publica los estudios en donde obtienen diferencias estadísticamente significativas",
       key.border.white=F,
       panel=myPanelFunc,
       auto.key.in = list(cex=1.5),
       ylab=NULL,
       scales = list(y = list(cex = 1.5))) 
```




© 2021 GitHub, Inc.
Terms
Privacy
Security
Status
Docs
Contact GitHub
Pricing
API
Training
Blog
About



